---
title: "Getting started with Applr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with Applr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4
)
```

A fitted linear model with more than one predictor lives in more dimensions
than a scatterplot can show. The usual workaround — `geom_smooth(method =
"lm")` — quietly fits a *different*, single-predictor model to the plotted
variables, so the line on the screen is not the model you summarized.

Applr draws the model you actually fit. Its core idea is the **slice**: hold
every predictor except one at a fixed value, and draw the model's predictions
as that one predictor varies. This vignette walks through the workflow on a
single dataset, `mtcars`.

```{r setup, message = FALSE}
library(Applr)
library(ggplot2)
```

## Fit a model, then autoplot() it

Start with a model where `mpg` depends on two predictors:

```{r}
model <- lm(mpg ~ disp + hp, data = mtcars)
lm_equation(model)
```

`autoplot()` is the quickest way to see it. It rebuilds the scatterplot from
the model's own data, picks the first numeric predictor for the x-axis, and
adds a slice line — with a subtitle recording which values the other
predictors were held at:

```{r}
autoplot(model)
```

The message tells you what happened: `hp` was not on an axis, so the line
holds it at its mean. Use `mapping = aes(x = ...)` to slice along a different
predictor, and pass any `geom_slice()` argument through `...`:

```{r}
autoplot(model, mapping = aes(x = hp), interval = "confidence")
```

## Build the plot yourself with geom_slice()

For full control, add `geom_slice()` to an ordinary ggplot. The layer reads
the plot's `aes()` to learn which predictor is on x, and predicts from your
model — no separate model is fit:

```{r}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point() +
  geom_slice(model)
```

### Choosing the slice

`predict_vars` pins the off-axis predictors to values you choose instead of
their means. Give a predictor several values and you get one line per value —
a small multiple of slices through the same model:

```{r}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point() +
  geom_slice(model, predict_vars = list(hp = c(66, 150, 335)))
```

### Intervals

`interval = "confidence"` or `"prediction"` shades the corresponding
`predict.lm()` interval around each line:

```{r}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point() +
  geom_slice(model, predict_vars = list(hp = 150), interval = "prediction")
```

## Labeling the slices

Three companion helpers describe the slices on the plot itself, so a reader
can tell which line is which and what was held constant.

`geom_slice_text()` labels the end of each line with its held value;
`geom_slice_caption()` writes the slice description under the plot:

```{r}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point() +
  geom_slice(model, predict_vars = list(hp = c(66, 150, 335))) +
  geom_slice_text() +
  geom_slice_caption()
```

(`geom_slice_subtitle()` is the third helper — it puts the model equation and
held values in the subtitle, and is what `autoplot()` uses by default.)

## Grouping and faceting

Slices respect the plot's grouping and faceting. With a model that includes
the grouping variable, each group gets its own correctly-sliced line:

```{r}
model_cyl <- lm(mpg ~ disp * cyl, data = mtcars)

ggplot(mtcars, aes(x = disp, y = mpg, color = factor(cyl))) +
  geom_point() +
  geom_slice(model_cyl)
```

## Where to go next

- `?geom_slice` covers the remaining options: projection bands (`band`),
  extending lines across the panel (`full_range`), transformed responses and
  `back_transform`, and the `n` resolution of the line.
- `?slice_2d` is the base-graphics equivalent of this whole workflow.
- `?scatter_3d` (or `autoplot(model, type = "3d")`) shows a two-predictor
  model as an interactive 3-D surface instead of a slice.
- `?lm_equation` and `?lm_latex` turn the fitted model into text or LaTeX for
  reports.
