```{r}
pacman::p_load(tidyverse)
devtools::load_all()

grades <- read_csv("testing/archive/Math425PastGrades.csv")

glimpse(grades)

plot(grades)

autoplot(lm(FinalExam ~ Midterm + Midterm:MagicTwoGroups, data = grades), color = "green")

model <- lm(FinalExam ~ Midterm + Midterm:MagicTwoGroups, data = grades)

ggplot(grades, aes(Midterm, FinalExam, color = factor(MagicTwoGroups))) +
  geom_point() +
  geom_slice(model)
```

```{r}
plot(grades, col = factor(grades$MagicTwoGroups))
```

```{r}
model <- lm(FinalExam ~ Midterm + Midterm:MagicTwoGroups, data = grades)

autoplot(model) +
  facet_wrap(~MagicTwoGroups)
```

```{r}

grades <- grades |> 
  mutate(
    MidtermGreaterThan70 = if_else(Midterm > 70, TRUE, FALSE)
  )

model <- lm(FinalExam ~ AssessmentQuizzes*MagicTwoGroups, data = grades)

summary(model)

ggplot(grades, aes(AssessmentQuizzes, FinalExam, )) +
  geom_point() +
  geom_slice(model) +
  facet_wrap(~MagicTwoGroups)
```


```{r}
set.seed(123)

n <- 60
x <- runif(n, -10, 10)
x2 <- sample(c(0,1,2), n, replace = TRUE)
x3 <- sample(c(0,1), n, replace = TRUE)
y <- x + 3 * x * x2 * x3 + rnorm(n)
dat <- data.frame(x, x2, x3, y)
model <- lm(y ~ x + x:x2:x3, data = dat)

ggplot(dat, aes(x, y, color = factor(x2), linetype = factor(x3))) +
  geom_point() +
  geom_slice(model)
```

```{r}
set.seed(123)

n <- 60
x <- runif(n, -10, 10)
x2 <- sample(c(0,1,2), n, replace = TRUE)
x3 <- sample(c(3,4,5), n, replace = TRUE)
y <- x + x2 + x3 + rnorm(n)
dat <- data.frame(x, x2, x3, y)
model <- lm(y ~ x + x2 + x3, data = dat)

ggplot(dat, aes(x, y, color = factor(x2), linetype = factor(x3))) +
  geom_point() +
  geom_slice(model)
```

```{r}
set.seed(123)
n <- 60
x <- runif(n, -10, 10)
x2 <- sample(c(0,2,4), n, 4)
x3 <- sample(c(0,1), n, 5)
y <- x + 3 * x2 + 2 * x3 + rnorm(n)
dat <- data.frame(x, x2, x3, y)
model <- lm(y ~ x + x2 + x3, data = dat)

autoplot(model, linetype = "dashed")

ggplot(dat, aes(x, y, color = factor(x2))) +
  geom_point() +
  geom_slice(model)

ggplot(dat, aes(x, y, color = factor(x2), linetype = factor(x3))) +
  geom_point() +
  geom_slice(model)

ggplot(dat, aes(x, y, color = factor(x2))) +
  geom_point() +
  geom_slice(model, interval="confidence")

ggplot(dat, aes(x, y)) +
  geom_point() +
  geom_slice(model, interval = "prediction")

ggplot(dat, aes(x, y)) +
  geom_point() +
  geom_slice(model, interval = "prediction", predict_vars = list(x2 = c(0, 2, 4)))

ggplot(dat, aes(x, y, color = factor(x2))) +
  geom_point() +
  geom_slice(model) +
  facet_wrap(~x3) +
  theme_minimal()

library(gganimate)

ggplot(dat, aes(x, y)) +
  geom_point() +
  geom_smooth() +
  geom_slice(model) +
  transition_time(x3) +
  ease_aes('linear')
# that didn't turn out so well. The geom_slice line isn't moving (and the points are? I didn't expect that.) I guess it's assuming each point is the same but at a different time, when in reality they are distinct. I was hoping to just move the prediction line.

```

```{r}
autoplot(lm(mpg ~ disp + hp, data = mtcars), type = "3d")
```



## Add

```{r}
# Expect: error - aes not implemented
autoplot(model, aes(color = MagicTwoGroups))
```

```{r}
# Expect: error - aes not implemented
ggplot(grades, aes(Midterm, FinalExam)) +
  geom_point() +
  geom_slice(model, aes(color = MagicTwoGroups))
```

```{r}
autoplot(model) +
  facet_wrap(~MagicTwoGroups)
```

```{r}
set.seed(123)

n <- 60
x <- runif(n, -10, 10)
x2 <- sample(c(0, 2, 4), n, replace = TRUE)
x3 <- sample(c(0, 1), n, replace = TRUE)
y <- x + 3 * x2 + 3 * x3 + rnorm(n)
dat <- data.frame(x, x2, x3, y)
model <- lm(y ~ x + x2 + x3, data = dat)

ggplot(dat, aes(x, y, color = factor(x2))) +
  geom_point() +
  geom_slice(model) +
  facet_wrap(~x3)

ggplot(dat, aes(x, y, color = factor(x2), linetype = factor(x3))) +
  geom_point() +
  geom_slice(model)
```


## Features


3. geom_slice is great for visualizing, and gives much quicker iteration that other methods, but it would be cool to have a more exploratory chart. What if we put sliders on all unmapped variables? It still hits defaults similar to geom_slice - and in every way behaves like geom_slice (we don't want inconsistencies in the package), but adds sliders for the hidden variables that aren't shown by color or facet or axis or linetype. Maybe even buttons for things like color by, but I'd need to feel that.
  - autoplot(model, sliders=TRUE)
  - autoplot(model, sliders=c(disp, cyl))
  - Those are built off of an implementation that can be used standalone
  - plotly seems like the way to go for this.
A few concerns: 
- how well can it integrate with this package as it stands (geom_slice, geom_slice_subtitle, geom_slice_text, geom_slice_band)
- how intuitive can it be to match the style of the ggplot functions?
- Will we have to make edits in two places every time geom_slice is modified (the ggplot and plotly implementations)
- What will the interface look like for these plotting functions? Both autoplot implementation and base plotly

7. Being able to do some animation where it slides or jumps through hidden values in the model would be super cool. gganimate seems to do something like this - but it also animates other things erroneously. It would be cool to render a gif that has just the linear model moving through slices in multidimensional space. That is one we'd have to consider what the interface would look like (what functions and arguments are available to the user) in connection with the backend feasibility and integration with other packages.
  
